\documentclass[]{cv}

\usepackage{amsmath}

\name{Andrei-Mihai Nicolae}
\address{https://nclandrei.com}
\contacts{nclandreimihai@gmail.com}

\begin{document}

	\makeheader
	
	\begin{cvsection}{Employment}
		\begin{cvsubsection}{Backend Developer}{Perigee}{September 2018 - Present}
		\end{cvsubsection}

		\begin{cvsubsection}{Software Developer}{New Verve Consulting}{November 2017 - June 2018}
			\begin{itemize}
				\item Designed, implemented and tested a greenfield plugin for the Jira Marketplace.
				\item Mainly worked on the backend of the application, written in Java, but was also involved 
				on the frontend of the plugin.
				\item Implemented efficient scripting solutions for clients in a timely fashion.
				\item Programming languages and technologies used were Java, Groovy, Velocity, Ajax, AWS, 
				Jira Server and Jira Service Desk Plugins.
			\end{itemize}
		\end{cvsubsection}
		
		\begin{cvsubsection}{Software Developer}{KnowledgeBomb}{October 2017 - June 2018}	
			\begin{itemize}
				\item Involved in the design, implementation and testing of a greenfield web application 
				providing services for tutors in the UK.
				\item Was the sole developer on the Go server which was capable of managing large pools of concurrent users 
				in an efficient manner.
				\item Worked on the implementation and testing of the frontend of the application.
				\item Managed and instrumented the whole infrastructure of the application on AWS (EC2 + ELB, DynamoDB, S3, Cognito, ECS + ECR)
				and Firebase Auth using Terraform.
				\item Programming languages and technologies used were Go, AngularJS, Jest, Docker, AWS, Firebase and Terraform.
			\end{itemize}
		\end{cvsubsection}
		
		\begin{cvsubsection}{Software Developer Intern}{King}{June - September 2017}
			\begin{itemize}
				\item Worked in the Gifting team as a full-stack developer.
				\item Implemented new features and maintained the legacy project but also developed most the backend for the new prototype that the team eventually launched.
				\item Programming languages and technologies used were Java, SQL, AngularJS + TypeScript, Docker, Jenkins, Mockito.
			\end{itemize}
		\end{cvsubsection}
		
		\begin{cvsubsection}{Junior Software Developer}{Avarix}{January - April 2017}
			\begin{itemize}
				\item Added features, solved bugs and maintained various financial trading platforms.
				\item Programming languages and technologies used were Scala, Akka, ConductR, ScalaTest, SQL.
			\end{itemize}
		\end{cvsubsection}

		\begin{cvsubsection}{Computer Science Demonstrator}{University of Glasgow}{September 2016 - May 2017}
			\begin{itemize}
				\item Explained and aided Computer Science basics and principles teaching to first year students as part of the Computer Science CS1PX and CS1CT courses.
				\item Programming languages used were Python and Alice.
			\end{itemize}
		\end{cvsubsection}

		\begin{cvsubsection}{Software Developer Intern}{King}{June - September 2016}
			\begin{itemize}
				\item Worked in the Gifting team that developed and maintained the whole flow through which the team could send gifts concurrently to up to tens of 
					millions of King games players throughout the world.
				\item Created a very large number of features that satisfied all usability and quality assurance tests, as well as solved a significant number of 
					both critical bugs that were in the active sprints or less major ones situated in the backlog.
				\item Have been involved in all stages of software development: requirements gathering, documentation, design, implementation, testing and feedback.
				\item Programming languages and technologies used were Java (JSON-RPC), Mockito, SQL, Docker, AngularJS, TypeScript.
			\end{itemize}
		\end{cvsubsection}

		\hspace{1pt}

		\begin{cvsubsection}{Summer Technology Analyst}{Morgan Stanley}{June - August 2015}
			\begin{itemize}
				\item Worked on the Exception Management System, implementing the main component which parsed the message, cached necessary fields and ran checks to ensure 
					data quality and completion, raising and storing exceptions where necessary.
				\item Created features for message communication between the UI and Middleware and synchronization among all tiers.	
				\item Enhanced the DB with Stred Procedures and UDFs, improving stability and efficiency.
				\item Have been involved in all the Software Development lifecycle phases: requirements gathering and analysis, design,
					implementation, testing and feedback.
				\item Programming languages and technologies used were Java (Spring environment), C, C++, SQL and SOAP.
			\end{itemize}
		\end{cvsubsection}

		\begin{cvsubsection}{Software Developer}{Google Summer of Code}{May - August 2014}
			\begin{itemize}
				\item Updated the CRAM code developed for the PR2 robot so the user can visualize the state belief of the 
				robot and the surrounding environment using Rviz instead of OpenGL.
				\item Created C++ libraries to provide functionalities for the robot, such as computing distance to objects 
				nearby or visualize different possible routes for accomplishing a goals and decide which one would be optimal.
				\item Programming languages used were Lisp, C++, Prolog.
			\end{itemize}
		\end{cvsubsection}

		\begin{cvsubsection}{Software Developer}{DFKI GmbH}{October 2013 - April 2014}
			\begin{itemize}
				\item Main tasks involved image processing, arm manipulation and object grasping.
				\item Developed algorithms to enhance robot movements and detect objects in highly cluttered environments (my
				choices have improved the time efficiency with 50-60\%)
				\item Programming languages used were C, C++ and Java.
			\end{itemize}
		\end{cvsubsection}

	\end{cvsection}
	
	\begin{cvsection}{Education}
		\begin{cvsubsection}{Glasgow, United Kingdom}{University of Glasgow}{September 2014 - June 2018}
			\begin{itemize}
				\item MSci in Software Engineering.
				\item Grade: First Class.
			\end{itemize}
		\end{cvsubsection}
		\begin{cvsubsection}{Bremen, Germany}{Jacobs University Bremen}{September 2013 - June 2014}
			\begin{itemize}
				\item BSc in Computer Science.
				\item Grade: 70\%.
			\end{itemize}
		\end{cvsubsection}

	\end{cvsection}
	
	\begin{cvsection}{Technical Experience}
		\begin{cvsubsection}{Projects}{}{}
			\begin{itemize}
				\item \textbf{DTSsistant} (2018 - Present). Building a Google Assistant app for the inhabitans of my hometown, 
				where people can get answers regarding whatever is happening around the city: 
				events, art exhibitions, trivia about the city etc.
				The REST API server is completely built in Go and is hosted on Google App Engine, while the NLP,
				intent extraction and parsing is done through DialogFlow.
				\item \textbf{SyncTube} (2018 - Present). Command line app that can sync the whole YouTube library of a user and download everything that was 
				either liked or added to a playlist since the last synchronization. Whole tool is being built in Go.
				\item \textbf{Go Ticket Guru} (2017-2018). Built a tool for concurrently fetching, storing and analyzing software tickets from 
				either Jira or Bugzilla. It can also automatically plot graphs after running the analysis, as well as perform different 
				statistical tests on the data. The whole tool was built in Go using BoltDB as database provider.
				\item \textbf{Palgo} (2016).  Electron app for visualizing and animating common algorithms such as Dijkstra’s algorithm for finding the 
				shortest path between two vertices in a graph.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Languages and Technologies}
		\begin{cvsubsection}{}{}{}	
			\begin{itemize}
				\item Go, Java, TypeScript, Rust, Bash. 
				\item Docker, Postgres, RabbitMQ, Prometheus, MongoDB, Redis, Elasticsearch, Kubernetes, Angular, Electron, Amazon Web Services, Google Cloud Platform, Terraform.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
\end{document}
